### 2014-09-06 related.tex
rw

The first to propose PTA are Smagardakis et al. \cite{yannis}. In their original work, both synchronization constraints and inter-thread dependencies are preserved, where inter-thread dependencies are respected by only allowing reorderings that leave the dependence structure exhibited by the original trace in tact. This ensures that the values of shared memory locations remain the same, which secures the soundness argument.

>>>>

Wang et al.~\cite{chao} pioneere the symbolic predictive analysis, which our approach also belongs to. However, the approach lacks support of heap encoding, therefore, cannot apply to real-world applications. The first PTA that applies to real-world applications are proposed by Smagardakis et al. \cite{yannis}. In their original work, both synchronization constraints and inter-thread dependencies are preserved, where inter-thread dependencies are respected by only allowing reorderings that leave the dependence structure exhibited by the original trace intact. This ensures that the values of shared memory locations remain the same, which secures the soundness argument.
